Parallelization of Fast $\ell_1$-Minimization for Face Recognition

### 2011-05-20 main.tex
removed what used to be figure 5

The results of this benchmark can be found in Figure \ref{fig:random_data}.
The x-axis represents the size of the $A$ matrix and the y-axis represents the
average amount of time it to complete a single problem instance.  The GPU
implementation tends to be faster than the CPU implementation at solving a
single large problem, whereas the the CPU implementation is faster at solving a
single small problem.  Figure \ref{fig:random_data2} shows the various sizes
and tolerances at which our GPU implementation begins to run faster than the
CPU implementation on synthetic data and will provide researchers with a
starting point of where to begin setting their tolerance levels for the ALM
algorithm.
\begin{figure}
\begin{center}
\includegraphics[width=3.5in]{results/random_data/time_vs_matrix_size_constant_tol}
\end{center}
\caption{Speed vs Dimensions of $A$.}
\label{fig:random_data}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=3.5in]{results/random_data/size_vs_speed_crossover_ratio_3}
\end{center}
\caption{Relation between CPU and GPU runtime vs tolerance level}
\label{fig:random_data2}
\end{figure}

>>>>

The results of this benchmark can be found in Figure \ref{fig:random_data}.
The x-axis represents the size of the $A$ matrix and the y-axis represents the
average amount of time it to complete a single problem instance.  The GPU
implementation tends to be faster than the CPU implementation at solving a
single large problem, whereas the the CPU implementation is faster at solving a
single small problem.  
\begin{figure}
\begin{center}
\includegraphics[width=3.5in]{results/random_data/time_vs_matrix_size_constant_tol}
\end{center}
\caption{Speed vs Dimensions of $A$.}
\label{fig:random_data}
\end{figure}
